---
title: Deliverable 1 
output: html_notebook
---

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

Start up code and loading R libraries: 

```{r}
#start up code 
#clear R
rm(list = ls())

#load the libraries 
library(scales)
library(ggplot2)
library(rio)
```

Laading in the data from Git Hub: 

```{r}
#load the data from github 
link="https://github.com/Many-Plots-Here/deliv1/raw/main/Best_Movie_by_Year_Netflix.csv"

MovieFile=import(link)
View(MovieFile)
```

Create an absolute values table: 
```{r}
absoluteT=table(MovieFile$MAIN_GENRE,
                exclude = 'nothing')

absoluteT
```

Turn aboslute values table into a prop table and then convert entries into percents:
```{r}
prop.table(absoluteT) #create prop table 

GenrePercent=prop.table(absoluteT)*100 #turn them into percents 
GenrePercent

```

Convert the frequency table into a data frame 
```{r}
tableFreq=as.data.frame(absoluteT) #turn the frequency table into a data frame 

names(tableFreq)=c("Genre", "Count") #rename data frame columns 

tableFreq$Percent=as.vector(GenrePercent) #add column for percentages 

tableFreq #view the table 
```
Data visualization prep: 
```{r}
#create the base 
base=ggplot(data = tableFreq,
            aes(x = Genre, 
                y = Percent))
```

Plot 1: input the data 
```{r}
#add layer that produces the main plot 
plot1 = base + geom_bar(fill = "gray",
                        stat = 'identity')
plot1
```

Plot 2: Add titles 
```{r}
#adding titles
titleText='Best Movies on Netflix in 2022'
sourceText= 'Source: Kaggle.com Netflix TV Shows and Movies (2022)'

#add layer that adds the titles
plot2 = plot1 + labs(title=titleText,
                     x = NULL,
                     y = NULL,
                     caption = sourceText
                     )
plot2
```

Plot 3: Add a horizontal line 
```{r}
#add a horizontal line
plot3 = plot2 + geom_hline(yintercept = 10,
                           linetype= "dashed",
                           size=1.5,
                           alpha=0.5)
plot3
```
Plot 4: Customize the vertical axes 
```{r}
#customize the vertical axes 
plot4 = plot3 + scale_y_continuous(breaks =  c(0, 5, 10, 20, 40),
                          limits = c(0, 45),
                          labels=unit_format(suffix = '%'))
plot4
```
Plot 5: Reposition the title and subtitle
```{r}
#reposition the title and subtitle
plot5 = plot4 + theme(plot.caption = element_text(hjust = 0), 
                      plot.title = element_text(hjust = 0.5))
plot5
```
Plot 6: Add value labels 
```{r}
#add values 
paste0(round(tableFreq$Percent,2), '%')
LABELS=paste0(round(tableFreq$Percent,2), '%')
###
plot6 = plot5 + geom_text(vjust=0, #hjust if flipping
                          size = 3,
                          aes(y = Percent ,
                              label = LABELS))
plot6

```
Ruruning the plots to have reordered bars:
```{r}
#ordering bars
tableFreq=tableFreq[order(tableFreq$Percent),]

(GenreOrd=tableFreq[order(tableFreq$Percent),'Genre'])

##adding this to the base 
LABELS=paste0(round(tableFreq$Percent,2), '%')
base= ggplot(data = tableFreq, 
             aes(x = Genre,y = Percent)) 
## adding these to base
base= base + scale_x_discrete(limits=GenreOrd) 
base= base + theme_classic()

#redo everything, copying from above 

#add layer that produces the main plot 
plot1 = base + geom_bar(fill = "gray",
                        stat = 'identity')

#adding titles
titleText='Best Movies on Netflix in 2022'
sourceText= 'Source: Kaggle.com Netflix TV Shows and Movies (2022)'

#add layer that adds the titles
plot2 = plot1 + labs(title=titleText,
                     x = NULL,
                     y = NULL,
                     caption = sourceText
)

#add a horizontal line
plot3 = plot2 + geom_hline(yintercept = 10,
                           linetype= "dashed",
                           size=1.5,
                           alpha=0.5)

#customize the vertical axes 
plot4 = plot3 + scale_y_continuous(breaks =  c(0, 5, 10, 20, 40),
                                   limits = c(0, 45),
                                   labels=unit_format(suffix = '%'))

#reposition the title and subtitle
plot5 = plot4 + theme(plot.caption = element_text(hjust = 0), 
                      plot.title = element_text(hjust = 0.5))

#add values 
paste0(round(tableFreq$Percent,2), '%')
LABELS=paste0(round(tableFreq$Percent,2), '%')
###
plot6 = plot5 + geom_text(vjust=0, #hjust if flipping
                          size = 3,
                          aes(y = Percent ,
                              label = LABELS))
plot6
```
```

Uploading to Git Hub: (?)

